cardinalR: Generating interesting high-dimensional data structures

### 2025-10-05 paper-cardinalR.Rmd
Removed on of branching projections

High-dimensional generalizations are provided by `gen_orglinearbranches(n, p, k)` and `gen_orgcurvybranches(n, p, k)` (`r knitr::asis_output(if (knitr::is_html_output()) { "Figure \\@ref(fig:branch) d-e"} else { "Figure \\@ref(fig:branch-proj) d-e"})`). Each branch is embedded in a unique or repeated $2\text{-}D$ subspace of the $p\text{-}D$ space. When `allow_share = TRUE`, multiple branches may share the same subspace; otherwise, subspaces are sampled without replacement until all possible $\binom{p}{2}$ combinations are exhausted, after which additional branches may repeat subspaces. Linear branches follow

@@

orglinearbranches_proj1 <- plot_proj(
  proj_obj = proj_obj1, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.65, 0.7), 
  title = "d1", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

@@

orglinearbranches_proj2 <- plot_proj(
  proj_obj = proj_obj2, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.7, 0.6), 
  title = "d2", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

@@

orglinearbranches_proj3 <- plot_proj(
  proj_obj = proj_obj3, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.5, 0.62), 
  title = "d3", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

@@

```{r}
orgcurvybranches_lang <- langevitour::langevitour(orgcurvybranches, levelColors = "black", enableControls = FALSE, width = "400px", height = "300px")
```

```{r orgcurvybranches-proj1}
scaled_data <- scale_data_manual(orgcurvybranches)

proj_obj1 <- get_projection(projection = projection, 
                            proj_scale = 1.2, 
                            scaled_data = scaled_data, 
                            axis_param = list(limits = 0.6,
                                              axis_scaled = 1.2, 
                                              axis_pos_x = -0.3, 
                                              axis_pos_y = -0.3, 
                                              threshold = 0.022))

orgcurvybranches_proj1 <- plot_proj(
  proj_obj = proj_obj1, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.4, 0.5), 
  title = "e1", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r orgcurvybranches-proj2}

orgcurvybranches_proj2 <- plot_proj(
  proj_obj = proj_obj2, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.7, 0.6), 
  title = "e2", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r orgcurvybranches-proj3}

orgcurvybranches_proj3 <- plot_proj(
  proj_obj = proj_obj3, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.5, 0.62), 
  title = "e3", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r branch, eval=knitr::is_html_output(), fig.cap="`langevitour` output  of the `expbranches`, `linearbranches`, `curvybranches`, `orglinearbranches`, and `orgcurvybranches` data in $4\\text{-}D$."}

branchfig <- bscols(
  htmltools::div(
    style = "display: grid; grid-template-columns: 1fr 1fr;",
    orglinearbranches_lang, orgcurvybranches_lang
  ),
  device = "xs"
)

@@

```{r branch-proj, eval=knitr::is_latex_output(), fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `expbranches` (a1-a3), `linearbranches` (b1-b3), `curvybranches` (c1-c3), `orglinearbranches` (d1-d3), `orgcurvybranches` (e1-e3) data.", fig.width=12, fig.height=8}

orglinearbranches_proj1 + orglinearbranches_proj2 + orglinearbranches_proj3 +
orgcurvybranches_proj1 + orgcurvybranches_proj2 + orgcurvybranches_proj3 +
  plot_layout(ncol = 3, guides = "collect") 
```

>>>>

High-dimensional generalizations are provided by `gen_orglinearbranches(n, p, k)` (`r knitr::asis_output(if (knitr::is_html_output()) { "Figure \\@ref(fig:branch)"} else { "Figure \\@ref(fig:branch-proj)"})`) and `gen_orgcurvybranches(n, p, k)`. Each branch is embedded in a unique or repeated $2\text{-}D$ subspace of the $p\text{-}D$ space. When `allow_share = TRUE`, multiple branches may share the same subspace; otherwise, subspaces are sampled without replacement until all possible $\binom{p}{2}$ combinations are exhausted, after which additional branches may repeat subspaces. Linear branches follow

@@

orglinearbranches_proj1 <- plot_proj(
  proj_obj = proj_obj1, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.65, 0.7), 
  title = "a1", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

@@

orglinearbranches_proj2 <- plot_proj(
  proj_obj = proj_obj2, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.7, 0.6), 
  title = "a2", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

@@

orglinearbranches_proj3 <- plot_proj(
  proj_obj = proj_obj3, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.5, 0.62), 
  title = "a3", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

@@

```{r branch, eval=knitr::is_html_output(), fig.cap="`langevitour` output  of the `orglinearbranches` data in $4\\text{-}D$."}

branchfig <- bscols(
  htmltools::div(
    style = "display: grid; grid-template-columns: 1fr 1fr;",
    orglinearbranches_lang
  ),
  device = "xs"
)

@@

```{r branch-proj, eval=knitr::is_latex_output(), fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `orglinearbranches` (a1-a3) data.", fig.width=12, fig.height=4}

orglinearbranches_proj1 + orglinearbranches_proj2 + orglinearbranches_proj3 +
  plot_layout(ncol = 3, guides = "collect") 
```

### 2025-10-05 paper-cardinalR.tex
Removed on of branching projections

High-dimensional generalizations are provided by \texttt{gen\_orglinearbranches(n,\ p,\ k)} and \texttt{gen\_orgcurvybranches(n,\ p,\ k)} (Figure \ref{fig:branch-proj} d-e). Each branch is embedded in a unique or repeated \(2\text{-}D\) subspace of the \(p\text{-}D\) space. When \texttt{allow\_share\ =\ TRUE}, multiple branches may share the same subspace; otherwise, subspaces are sampled without replacement until all possible \(\binom{p}{2}\) combinations are exhausted, after which additional branches may repeat subspaces. Linear branches follow

@@

\begin{figure}[!]
\includegraphics[width=1\linewidth]{paper-cardinalR_files/figure-latex/branch-proj-1} \caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `expbranches` (a1-a3), `linearbranches` (b1-b3), `curvybranches` (c1-c3), `orglinearbranches` (d1-d3), `orgcurvybranches` (e1-e3) data.}\label{fig:branch-proj}
\end{figure}

>>>>

High-dimensional generalizations are provided by \texttt{gen\_orglinearbranches(n,\ p,\ k)} (Figure \ref{fig:branch-proj}) and \texttt{gen\_orgcurvybranches(n,\ p,\ k)}. Each branch is embedded in a unique or repeated \(2\text{-}D\) subspace of the \(p\text{-}D\) space. When \texttt{allow\_share\ =\ TRUE}, multiple branches may share the same subspace; otherwise, subspaces are sampled without replacement until all possible \(\binom{p}{2}\) combinations are exhausted, after which additional branches may repeat subspaces. Linear branches follow

@@

\begin{figure}[!]
\includegraphics[width=1\linewidth]{paper-cardinalR_files/figure-latex/branch-proj-1} \caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `orglinearbranches` (a1-a3) data.}\label{fig:branch-proj}
\end{figure}
